Modern Graph Generators: A Survey

### 2018-10-08 comparison.tex
Unification fo terminology

\begin{itemize}
\item Characteristics of the \textbf{domain} -- its \textit{type} (fixed, specified using a schema, or extracted from input data) and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain,
\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Upd.''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key \textbf{configuration} options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
    \item \textit{output format} (column ``Output'') of the produced graph, and
    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
  \end{itemize}
\end{itemize}

@@

   & R-Mat & -- & -- & Y & N & Y & power-law & edge-list &  N  \\

@@

  & HPC Scal. Graph Anal. & fixed & & Y & N& N& uniform &edge-list & N   \\

@@

\paragraph{Number of Generators, Size and Output Format of the Data}
As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic. None of these generators is natively implemented in a distributed manner and thus generating  output at the Big Data scale. On the other hand, Linked Open Data (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.

The second large group of generators also corresponds to a popular application domain -- social networks. In this case the size of the output graph is important if we require realistic features of the output. However, most of the proposals do not provide an implementation at all and, thus, this aspect cannot be discussed reliably.

@@

\paragraph{Operations}
In the case of operations, most commonly the respective generators are accompanied with a set of fixed read operations or sequences of operations representing typical behavior of a user. In some cases this aspect is more flexible -- either query templates are used or the operations are generated, e.g., in order to access most of the data. On the other hand, update operations are provided only in a small amount of cases. As we will discuss in Section~\ref{sec:evolving}, the more general problem of evolving graphs is still an open issue.

\paragraph{Configuration}
A natural feature of the generators is to provide as realistic result as possible. Hence, most of them focus not only on the structure of the output graph, but also the properties. For the purpose of generating graphs with near real-world characteristics various distributions are used, such as power-law, Zipfian etc. Especially interesting are distributions extracted from real-wold data (such as, e.g., Facebook in case of social network domain).

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & \\
\cline{2-8}
   & R-Mat    & {\bf x} & & & & x & \\
\cline{2-8}
  & GraphGen  & {\bf x} & & x & & & \\
\cline{2-8}
  & Graph 500 & {\bf x} & & & & x & \\
\cline{2-8}
  & BTER      & {\bf x} & & & & & \\
\cline{2-8}
  & Darwini   & {\bf x} & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & \\
\cline{2-8}
 & LBBM  & & {\bf x} & & & & \\
\cline{2-8}
 & UOBM  & & {\bf x} & & & & \\
\cline{2-8}
 & IIMB & & {\bf x} & & & & \\
\cline{2-8}
 & BSBM & & {\bf x} & & & & \\
\cline{2-8}
 & SP$^2$Bench & & {\bf x} & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
\cline{2-8}
 & DBPSB & & {\bf x} & & & & \\
\cline{2-8}
 & LODIB & & {\bf x} & & & & \\
\cline{2-8}
 & SIB & & {\bf x} & & & & \\
\cline{2-8}
 & Geographica & & {\bf x} & & & & \\
\cline{2-8}
 & WatDiv & & {\bf x} & & & & \\
\cline{2-8}
 & RBench & & {\bf x} & & & & \\
\cline{2-8}
 & LDBC SPB & & {\bf x} & & & & \\
\cline{2-8}
 & LinkGen & & {\bf x} & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & \\
\cline{2-8}
  & gMark & & x & {\bf x} & x & & \\
\cline{2-8}
  & graphGen & & & {\bf x} & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & {\bf x} & & \\
\cline{2-8}
 & LinkBench  & & & x & {\bf x} & & \\
\cline{2-8}
 & S3G2  & & x & x & {\bf x} & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & {\bf x} & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & \\
\cline{2-8}
  & Graphalytics & & & & & {\bf x} & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & {\bf x}\\
\cline{2-8}
  & RSPLab & & & & & & {\bf x} \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

For example, many general or domain-agnostic graph generators such as the
preferential attachment, RMAT or Graph500, are typically used to test graph
analytics frameworks when large real graphs are not available. Actually,
Graphalytics uses RMAT as one as its graph generators for benchmarking graph
analytics.

>>>>

\begin{itemize}
\item Characteristics of the \textbf{domain} -- its \textit{type} (column ``Type''), i.e.,  fixed, specified using a schema, or extracted from input data and the particular \textit{target} domain, or, in case of a generic tool, the chosen sample domain (column ``Target/sample''),
\item Characteristics of \textit{read}/\textit{update} \textbf{operations} (columns ``Read'' and ``Upd.''), i.e., whether the set of operations is fixed/generated, if it involves operation mixes (i.e., sets/sequences of operations), or if templates of operations are supported.
\item Key \textbf{configuration} options:
  \begin{itemize}
    \item whether the generator deals only with structure, or also with \emph{properties} (column ``Pro.'') of the graph (Y/N feature),
    \item supported types of \emph{distributions} (column ``Distributions'') used for generating of the data,
    \item \textit{output format} (column ``Output'') of the produced graph, and
    \item  whether the generator is \textit{distributed} (column ``Dis.'') and thus enables more efficient data generation (Y/N feature).
  \end{itemize}
\end{itemize}

@@

   & R-MAT & -- & -- & Y & N & Y & power-law & edge-list &  N  \\

@@

  & HPC Scal. Graph Anal. & fixed & -- & Y & N& N& uniform &edge-list & N   \\

@@

\paragraph{Number of Generators, Size and Output Format of the Data}
As we can see, the biggest set of available generators can be found in the Semantic Web application domain, probably due to its recent popularity and a number of research groups dealing with this topic. None of these generators is natively implemented in a distributed manner and thus primarily generating  output at the Big Data scale. On the other hand, Linked Open Data (LOD) is expected to be large in general, however this is the case of the whole \emph{LOD Cloud}\footnote{\url{https://lod-cloud.net/}}, but not necessarily of the particular data sets forming it.

The second large group of generators also corresponds to a popular application domain -- social networks. In this case the size of the output graph is important if we require realistic features of the result. However, most of the proposals do not provide an implementation at all and, thus, unfortunately this aspect cannot be discussed reliably.

@@

\paragraph{Operations}
In the case of operations, most commonly the respective generators are accompanied with a set of fixed read operations or sequences of operations (query mixes) representing typical behavior of a user. In some cases this aspect is more flexible -- either query templates are used or the operations are generated, e.g., in order to access most of the data in the generated graph. On the other hand, update operations are provided only in a small amount of cases. As we will discuss in Section~\ref{sec:evolving}, the more general problem of evolving graphs is still an open issue.

\paragraph{Configuration}
A natural feature of the generators is to provide as realistic result as possible. Hence, most of them focus not only on the structure of the output graph, but also the properties. For the purpose of generating graphs with near real-world characteristics various distributions are used, such as power-law, Zipfian etc. Especially interesting are distributions extracted from real-wold data (such as, e.g., Facebook in case of the social network domain).

@@

\begin{table}
\scriptsize
\centering
\tbl{Overlapping of classes of generators} {
\begin{tabular}{| c | l | l | l | l | l | l | l | }
 \hline
           &  \textbf{Generator}
               & \textbf{\rot{General}}
               & \textbf{\rot{Semantic Web}}
               & \textbf{\rot{Graph databases\ }}
               & \textbf{\rot{Social networks}}
               & \textbf{\rot{Analytics}}
               & \textbf{\rot{Steaming}}
               \\ \hline
\hline   % ====================== general graphs
\multirow{6}{*}{\rot{\textbf{General}}}
  & \cite{Barabasi99emergenceScaling} & {\bf x} & & & & x & \\
\cline{2-8}
   & R-MAT    & {\bf x} & & & & x & \\
\cline{2-8}
  & GraphGen  & {\bf x} & & x & & & \\
\cline{2-8}
  & Graph 500 & {\bf x} & & & & x & \\
\cline{2-8}
  & BTER      & {\bf x} & & & & & \\
\cline{2-8}
  & Darwini   & {\bf x} & & & & & \\
\hline
\hline %  ======================  Semantic web
\multirow{15}{*}{\rot{\textbf{Semantic web}}}
 & LUBM  & & {\bf x} & & & & \\
\cline{2-8}
 & LBBM  & & {\bf x} & & & & \\
\cline{2-8}
 & UOBM  & & {\bf x} & & & & \\
\cline{2-8}
 & IIMB & & {\bf x} & & & & \\
\cline{2-8}
 & BSBM & & {\bf x} & & & & \\
\cline{2-8}
 & SP$^2$Bench & & {\bf x} & & & & \\
\cline{2-8}
 & \cite{Duan:2011:AOC:1989323.1989340} & & {\bf x} & & & & \\
\cline{2-8}
 & DBPSB & & {\bf x} & & & & \\
\cline{2-8}
 & LODIB & & {\bf x} & & & & \\
\cline{2-8}
 & SIB & & {\bf x} & & & & \\
\cline{2-8}
 & Geographica & & {\bf x} & & & & \\
\cline{2-8}
 & WatDiv & & {\bf x} & & & & \\
\cline{2-8}
 & RBench & & {\bf x} & & & & \\
\cline{2-8}
 & LDBC SPB & & {\bf x} & & & & \\
\cline{2-8}
 & LinkGen & & {\bf x} & & & & \\
\hline
\hline  % ======================  graph databases
\multirow{3}{*}{\rot{\textbf{GDBs}}}
  & XGDBench & & & {\bf x} & x & & \\
\cline{2-8}
  & gMark & & x & {\bf x} & x & & \\
\cline{2-8}
  & graphGen & & & {\bf x} & & & \\
\hline
\hline %  ======================   social networks
\multirow{7}{*}{\rot{\textbf{SNs}}}
 & \cite{Barrett:2009:GAL:1995456.1995598} & & & & {\bf x} & & \\
\cline{2-8}
 & \cite{Yao2011}  & & & & {\bf x} & & \\
\cline{2-8}
 & LinkBench  & & & x & {\bf x} & & \\
\cline{2-8}
 & S3G2  & & x & x & {\bf x} & & \\
\cline{2-8}
 & \cite{Sukthankar-SocialInfo2014}  & & & & {\bf x} & & \\
\cline{2-8}
 & LDBC SNB   & & x & x & {\bf x} & & \\
\cline{2-8}
  & \cite{Nettleton2016}  & & & & {\bf x} & & \\
\hline
\hline   % ======================   graph analytics
\multirow{2}{*}{\rot{\textbf{An.}}}
  & HPC Scal. Graph Anal.  & & & & & {\bf x} & \\
\cline{2-8}
  & Graphalytics & & & & & {\bf x} & \\
\hline
\hline   %  ======================  streaming
\multirow{2}{*}{\rot{\textbf{St.}}}
  & S2Gen & & & & & & {\bf x}\\
\cline{2-8}
  & RSPLab & & & & & & {\bf x} \\
%\cline{2-8}
%  & & & & & & \\
\hline
\end{tabular} }
\label{tab:overlapping}
\end{table}

For example, many general or domain-agnostic graph generators such as the
preferential attachment~\cite{Barabasi99emergenceScaling}, R-MAT or Graph 500, are typically used to test graph
analytics frameworks when large real graphs are not available. Actually,
Graphalytics uses R-MAT as one as its graph generators for benchmarking graph
analytics.

### 2018-10-08 generators_general.tex
Unification fo terminology

\paragraph {R-Mat} (\emph{R}ecursive \emph{Mat}rix) R-Mat is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
The generator is recursive and uses only a small number of parameters.
In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-Mat is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-Mat can generate weighted, directed and bipartite graphs.

>>>>

\paragraph {R-MAT} (\emph{R}ecursive \emph{Mat}rix) R-MAT is a procedural synthetic graph generator which is designed to generate power-law degree
distributions~\cite{DBLP:conf/sdm/ChakrabartiZF04}.
The generator is recursive and uses only a small number of parameters.
In principle, the strategy of this generator is to find simple mechanisms to generate graphs that match
the properties of the real graphs. In particular, the design goals of R-MAT is to generate graphs that match the degree distributions, imitate a community structure and have a small diameter. R-MAT can generate weighted, directed and bipartite graphs.
